---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit the README.Rmd file -->


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Lab report #1

Follow the instructions posted at https://ds202-at-isu.github.io/labs.html for the lab assignment. The work is meant to be finished during the lab time, but you have time until Monday evening to polish things.

Include your answers in this document (Rmd file). Make sure that it knits properly (into the md file). Upload both the Rmd and the md file to your repository.  

All submissions to the github repo will be automatically uploaded for grading once the due date is passed.
Submit a link to your repository on Canvas (only one submission per team) to signal to the instructors that you are done with your submission.
```{r}
#Dependencies
library(classdata)
library(ggplot2)
```


**Step 1 Result:**
```{r}
#Look at the first couple rows of dataset
head(ames)
```


```{r}
#Look at the structure
str(ames)
```
```{r}
# Summary function to find range (mins and maxes) of each variabel
summary(ames)
```

As a team, we found that there are 16b variables total, which include Parcel ID, Address, Style, Occupancy, Sale Date, Sale Price, Multi Sale, YearBuilt, Acres, TotalLivingArea, Bedrooms, FinishedBsmtArea, LotArea, AC, FirePlace, and Neighborhood. The types of variables include factors, dates, numerical, and characters, with each variable describing a different aspect of an individual house. The expected data range can be found in the summary table for each variable. 

**Step 2 Result:**
As a team, we found that

Sale price is off special interest because it's the main factor people look at when buying a house. Other factors that could influences are LotArea, Bedrooms, Year the house was built. These are some factors that are also special since they could influence the most important variable which is Sale Price. 

**Step 3 Result:**
```{r}
ggplot(ames, aes(x = `Sale Price`)) + geom_histogram(binwidth = 2000000, fill = "blue") + ggtitle("Histogram of Sales Price")
```

As a team, we found that the main variable is Sale Price. The range of sale price is $20,500,000 (Min = 0, Max = 20,500,000). According to our histogram, it would appear that a majority of houses were sold for under $2,000,000. There appear to be some outliers priced at above $10,000,000.

**Step 4 Result:**
